### 2009-04-02 docs/eos_notes/eos_notes.tex
removed the call to make_explicit_thermal in step 8, and instead store the results from the call to make_explicit_thermal in step 4 since they were computing exactly the same thing.  Cuts down on another eos call with no changes to results or peak memory usage
consolidated calls to make_thermal_coeffs so we don't repeat the same calculations twice.  cuts about 7% off runtime

\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 

@@

\item In {\tt thermal\_conduct}, we compute the coefficients for 

@@

\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 

@@

\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$ and $(\rho,T,X)^{(2),*}$.

@@

\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
\item In {\tt thermal\_conduct}, we compute the coefficients for 

@@

\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$ and $(\rho,T,X)^{(2),*}$.

>>>>

\item In {\tt advance} before {\tt make\_explicit\_thermal}, we compute the coefficients for 

@@

@@

@@

\item In {\tt advance} before {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(2),*}$.

@@

\item In {\tt advance} before {\tt make\_explicit\_thermal}, we compute the coefficients for 

@@

\item In {\tt advance} before {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(2),*}$.
